\documentclass[11pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\noindent {\huge\textbf{Mintu Agarwal}}
\end{flushleft}
2nd Year Undergraduate  \hfill\textbf{Email : }in.mail.mintu@gmail.com
\\Department of Industrial and Systems Engineering \hfill\textbf{Phone : }+91-8697936981
\vspace{-6pt}
\\
\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\
\hline
\centering{2018} - Present & \centering{B.Tech} & \centering{Indian Institute of Technology, Kharagpur} & 9.25/10\\
\hline
\centering{2018} & \centering{CBSE(\Romannum{12})} & \centering{Hariyana Vidya Mandir, Kolkata} & 90.2$\%$\\
\hline
\centering{2016} & \centering{WBBSE(\Romannum{10})} & \centering{Gyan Bharati Vidyapith, Kolkata} & 90$\%$\\
\hline
\end{tabular}
\end{center}
{\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}
\begin{itemize}
\item Currently holding Department Rank 3$^{rd}$ among 70 students of Industrial and Systems Engineering Department, IIT Kharagput at the end of UG 2$^{nd}$ Year.
\item Secured \textbf{All India Rank 6964} in \textbf{JEE Advanced 2018} among the 2.2 Lakh shortlisted candidates.
\iffalse
\item Received the \textbf{Academic Excellence Award} for exceptional academic performance in 2015-16 academic session.
\fi
\item Among the top 1\% of the 1.05 million applicants in JEE Mains 2015.
\item Secured \textbf{General Merit Rank of 243} in \textbf{WBJEE 2018} among 1.25 Lakh candidates.
\item Participated in \textbf{State Level Camp} of Vidyarthi Vigyan Manthan 2017 Program conducted by Vigyan Prasar and Vigyan Bharati.
\item Secured Department Change to Industrial and Systems Engineering by acquiring a CGPA of \textbf{9.27} at the end of UG 1$^{st}$ Year.
\item \textbf{1$^{st}$ Runner Up} in Image Processing Event, Crusade during Kshitij'19 at IIT Kharagpur.
\item Peak rating of \textbf{1957 on CodeChef} platform, \textbf{1719 on Codeforces}
\item Acquired \textbf{Global Rank 996} among 8200 particpants in Google Kickstart 2020(Round D).  
\item Acquired \textbf{Rank 44} in \textbf{HackerRank} Hack the Interview VI(Asia Pacific) contest.
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Key Projects}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Simulation and Schedule-generation for an Assembly Line}  \\\textbf{Mentor: }\textbf{Prof. Goutam Sen}, Department of Industrial and Systems Engineering.\hfill\hfill(\textit{Mar'20- Ongoing})
\begin{itemize}
\item Team Project for simulating a Virtual Reality Environment of automated Hydraulic-excavators assembly using 3D Model developed on SketchUp with Unity3D or Unreal-Engine measuring safety levels for generated schedule.
\item Study and Implementation of Ant-Colony Optimization Algorithm which returns the ordered sequence of sites for operations during assembly.
\end{itemize}
\end{itemize}
\vspace{-2mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Programming Languages: }C, C++, Python, HTML5, CSS
\item \textbf{Software and Libraries: } MATLAB, CPLEX, numpy, scipy, pandas, matplotlib, Solidworks, SketchUp, OpenCV, MySQL, Sublime Text
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Student Mentor at GOC-CP Mentor-Mentee Program}\hfill\hfill(\textit{Mar'2020-present})
\begin{itemize}
\item Mentor to \textbf{6 freshmen} students, solving their Competitive Programming related doubts. 
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}
\item \textbf{Volunteer, National Service Scheme}\hfill\hfill(\textit{Aug'18-Mar'20})
\begin{itemize}
\item Managed a group of NSS Unit members during the NSS Annual Camp 2018.
\item Conducted Donation-drive under Unit coordinator for Relief Funds started for states struck by natural calamities.
%\item Acted as a link between Placement core team, companies and Students during placement process.
\end{itemize}
\vspace{1mm}
\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Relevant Courses}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{9.8cm}|p{9.8cm}|}
\hline
Design and Analysis of Algorithms & Algorithms Laboratory\\
Operations Research-I &  Linear Algebra\\
Probability and Statistics & Information Systems and Design Lab\\
Basic Electronics & Basic Economics  \\
Operations Research - II & Operations Research Laboratory\\ 
\hline
\end{tabular}
\end{center}
%\medskip
%\newpage
%\end{itemize}
\iffalse
{\large \textbf{\begin{tcolorbox}\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\item Achieved the title of \textbf{expert} with maxmimum rating of \textbf{1719} on Codeforces platform for Competitive Programming.
\item 1st Runner Up in Image Processing Event, Crusade during Kshitij'19 at IIT Kharagpur.
\item \textbf{4-star} Division-1 programmer on Codechef platform with maximum rating of \textbf{1957}.
\end{itemize}
\fi
\end{document}